---
title: "Packages"
subtitle: "R packages for data science"
title-block-banner: "#F8EFE7"
title-block-banner-color: "#934C12"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, include=FALSE}
library(htmltools)
source("../../R/functions.R")
```


::: {.column-body-outset}

::: {layout-ncol="2"}
::: {.centre-it style="margin-top:auto; margin-bottom:auto;"}
```{r}
create_proj_card(
  img_src = "../images/galah_logo.png",
  url = "https://galah.ala.org.au/",
  title = "galah"
)
```
:::

[**galah**](https://galah.ala.org.au/) \
The galah package uses tidy syntax to download biodiversity data from GBIF, the ALA, and other Living Atlases.
:::

::: {layout-ncol="2"}
::: {.centre-it style="margin-top:auto; margin-bottom:auto;"}
```{r}
create_proj_card(
  img_src = "../images/corella-logo.png",
  url = "https://corella.ala.org.au/",
  title = "corella"
)
```
:::

[**corella**](https://corella.ala.org.au/) \
The corella package helps users standardise their data using the [Darwin Core Standard](https://dwc.tdwg.org/). The package centres around `set_` functions, which are wrappers around `dplyr::mutate()` and let users add or modify columns with helpful suggestions and data checks.
:::

::: {layout-ncol="2"}
::: {.centre-it style="margin-top:auto; margin-bottom:auto;"}
```{r}
create_proj_card(
  img_src = "../images/galaxias-logo.png",
  url = "https://galaxias.ala.org.au/",
  title = "corella"
)
```
:::

[**galaxias**](https://corella.ala.org.au/) \
The galaxias package lets people describe, bundle, and share biodiversity information using the [Darwin Core Standard](https://dwc.tdwg.org/). The package mirrors funtionality in devtools, usethis and dplyr.
:::

::: {layout-ncol="2"}
::: {.centre-it style="margin-top:auto; margin-bottom:auto;"}
```{r}
create_proj_card(
  img_src = "../images/delma-logo.png",
  url = "https://delma.ala.org.au/R/",
  title = "corella"
)
```
:::

[**delma**](https://delma.ala.org.au/) \
The delma package converts metadata statements written in R Markdown or Quarto markdown to Ecological Metadata Language (EML).
:::

:::
